Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
chore: put simulations image
chore: improve approach description

The feature vector $o_v$ of which is composed the graph $G'_t$ used by the policy $\pi_{gnn}$ is described by:
 $o_v = (\theta^v_t, \omega)$. \lukas{we used $o_v$ to describe the observation of node $v$ in section II.C - so this would not include field information, right?}

@@

The policy $\pi_{gnn}$ is then evaluated for each node, 

@@

 we use a value-based approach combined with a \ac{GNN} as a function approximator.

@@

Specifically, we leveraged the property of \ac{GNN}s to have a dual interpretation, i.e., to function globally over the entire graph and locally only over the neighbourhood. 

@@

  \item experience replay stores experiences in the form of \emph{graphs},

@@

 the use of \acp{GNN} allows us to define policies on a variable neighbourhood  that is essential in such systems as this can vary based on the neighbourhood policy,

@@

\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal.

>>>>

From this field, we construct the feature vector $f_v$ for each node $v$ in $G_t$ as follows:
 $f_v = (\theta^v_t, o^t_v)$. \lukas{we used $o_v$ to describe the observation of node $v$ in section II.C - so this would not include field information, right?}

@@

The policy $\pi_{gnn}$ is then evaluated for each node using $f_v$ as input, 

@@

 we use a \emph{value-based} approach combined with a \ac{GNN} as a function approximator.

@@

Specifically, we leveraged the property of \ac{GNN}s to have a dual interpretation, 
 i.e., to function globally over the entire graph and locally only over the neighbourhood. 

@@

  \item experience replay stores experiences in the form of \emph{graphs} decorated with features (e.g., observations, actions, rewards, etc.),

@@

 the use of \acp{GNN} allows us to define policies on a variable neighbourhood 
 that is essential in such systems as this can vary based on the neighbourhood policy,

@@

\section{Evaluation}
\label{sec:eval}

%% Put three subfigures of simulations, start, after, end
\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/start.png}
      \caption{Initial state}
      \label{fig:initial}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/after.png}
      \caption{After 50 steps}
      \label{fig:after}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/end.png}
      \caption{After 200 steps}
      \label{fig:end}
  \end{subfigure}
  \caption{Simulation of the proposed approach. 
  The dots represent the robots, 
  the circle area on the top right represent the phenomenon to be monitored, 
  and the gray area represent the area covered by the robots.}
  \label{fig:simulations}
\end{figure}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal.
